An Efficient Interpolation Technique for Jump Proposals in Reversible-Jump Markov Chain Monte Carlo Calculations

### 2011-03-17 paper.tex
Change to V.

An example of a multi-modal parameter space where chains can get stuck
on high-posterior islands comes from antipodal sky location
degeneracies for networks of three ground-based gravitational-wave
interferometers or for low-frequency gravitational wave signals in the
proposed space-borne instrument LISA \cite{LISA}.  Although PDFs
produced by MCMC chains will generally show both locations on the sky,
the chain length may not be sufficiently long in practice to include
enough jumps between the two high-likelihood antipodal locations.  In
general, the relative weight of two separated peaks is determined with
a fractional error that scales as
$1/\sqrt{N_{\textnormal{transitions}}}$, where
$N_{\textnormal{transitions}}$ is the number of transitions between
the peaks.  By increasing the number of proposed transitions, the
convergence of such PDFs can be enhanced using the kD tree
interpolated proposal.

>>>>

An example of a multi-modal parameter space where chains can get stuck
on high-posterior islands comes from antipodal sky location
degeneracies for networks of three ground-based gravitational-wave
interferometers or for low-frequency gravitational wave signals in the
proposed space-borne instrument LISA \cite{LISA}.  Although PDFs
produced by MCMC chains will generally show both locations on the sky,
the chain length may not be sufficiently long in practice to include
enough jumps between the two high-likelihood antipodal locations.  In
general, the relative weight of two separated peaks is determined with
a fractional error that scales as
$1/\sqrt{N_{\textnormal{transitions}}}$, where
$N_{\textnormal{transitions}}$ is the number of transitions between
the peaks.  By increasing the number of proposed transitions, the
convergence of such PDFs can be enhanced using the kD-tree
interpolated proposal.  As described above, one could test the convergence of the PDF 
by running a followup MCMC with a jump proposal
distribution from an interpolation of the first original PDF.  This
follow-up MCMC would attempt large global jump proposals rather than
small local ones, meaning that it could rapidly accumulate sufficient
points to determine whether the original run spent the correct fractional
amounts of time in the various modes.
